Mechanising Recursion Schemes with Magic-Free Coq Extraction

### 2024-10-10 paper/paper.tex
minor

In the context of Coq, Danvy explains the use of fold/unfold lemmas to mechanize
equational reasoning about recursive programs~\cite{DANVY_2022}. Fold-unfold
lemmas enable optimizations like fusion by allowing programs to be
systematically simplified, including eliminating intermediate structures.
Additionally, an approach to deforestation called the worker/wrapper
transformation~\cite{gill09} was formalised and mechanised in
Agda~\cite{SCULTHORPE_HUTTON_2014}.

>>>>

In the context of Coq, Danvy explains the use of fold/unfold lemmas to mechanize
equational reasoning about recursive programs~\cite{DANVY_2022}. Fold-unfold
lemmas enable optimizations like fusion by allowing programs to be
systematically simplified, including eliminating intermediate structures.
Additionally, an approach to fusion called the worker/wrapper
transformation~\cite{gill09} was formalised and mechanised in
Agda~\cite{SCULTHORPE_HUTTON_2014}.
